TITLE

### 2021-02-26 outputs/Paper.Rmd
histogram update

>>>>

```{r salary_distribution, echo=FALSE}
ggplot(simulated_data, aes(x = simulated_data$Q9, fill=type)) +
  geom_histogram(position = "dodge", bins = 30,binwidth = 0.5) +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title="The Salary Distributions was higher for Teatment Group", x="Salary", y="Number of employee")+
  geom_density()
